### 2009-12-06 src/Docs/Intro.tex
Recommended readings for the Desc universe.

>>>>

Concerning the |Desc| universe, Morris et al. \cite{morris:spf} wrote
a clear article, covering that topic and much more. In particular,
they show why and how |Box| and |mapBox| can automatically derived
from |Desc|. Conor's work on Ornamemts \cite{mcbride:ornaments} builds
up from a simplified |Desc| universe: some insights can be found there
too. Finally, the authoritative source shall be cited: Dybjer et
al. on induction-recursion \cite{dybjer:ir_axiom, dybjer:ir_algebra,
  dybjer:iir}.
